A geo-referenced micro-data set of real estate listings for Spain's three largest cities

### 2023-10-18 editorial-materials/EPB-2022-0116.R1_response_to_reviewer.Rmd

<!--
```{r install-data-package, include = FALSE}
# Run only once if needed to install data package `sobiEquity`
if (!require("idealista18", character.only = TRUE)) {
devtools::install_github("https://github.com/paezha/idealista18")
}
```

```{r setup,  cache=FALSE, warning = FALSE, include=FALSE, message = FALSE}
library(idealista18)
library(tidyverse)

set.seed(1234)
```
-->

To the Editor:

We have responded to the comments of the reviewers in a thorough and conscientious manner. This has made the paper longer.

At this point, the paper has been stuck in limbo for months with the Editorial Assistant, who initially requested that we cut the length of the paper, but did not indicate just _what_ to cut. In our opinion, the paper needs to be seen by an Editor to decide whether the paper _needs_ to be cut, and if so, _what_ can be left out without compromising the changes made to satisfy the requests of the reviewers.

More generally, to avoid this situation in the future with Data Papers, the editors need to:

1. Instruct reviewers as to the expectations for criticism. If the papers cannot be longer, they should not ask questions that require long responses; and/or
1. Instruct the Editorial Assistant that papers _will be_ longer after revisions; and/or
1. Provide clear guidelines to the authors to ensure that they know what is essential to revise so that they do not spend time and effort responding to critiques that the Editors may find superfluous.

Below are our detailed responses to the comments from the Reviewers.

### 2024-03-12 EPB/main_EPB.Rmd
Prepared files for final submission to production with EPB

```{r load-packages, include=FALSE}
library(dplyr)
library(ggplot2)
library(glue)
library(gridExtra)
library(idealista18)
library(kableExtra)
library(xtable)
library(sf)
```

@@

This micro-data set can be used to benchmark new methods in a reproducible fashion  [e.g., @rey2023using]. Applied and theoretical researchers on real estate mass appraisal and valuation methods might use this dataset to canonically compare the performance of their proposed comparable and hedonic models, among others. The data can also be used to study the segmentation of housing submarkets and related topics such as the impact of suburban areas on house prices. The listings have been enriched with official information from the Spanish cadastre along with other relevant geographical features, such as distance to urban points of interest. In any case, the data might be easily extended by spatially joining other datasets that contain information at administrative, census tract, or postal code levels.

@@

plot6 <- ggplot(data = Valencia_prop) +
  geom_sf(aes(fill = Quantile),
          color = NA,
          size=.2) +
    geom_sf(data = Valencia_Polygons,
          fill = NA) +
  labs(caption = "Valencia districts: listings/total dwellings") +
  ylim(39.405,39.52) +
  theme_bw(base_size = 6) +
  scale_fill_manual(values=c("#FFFEDE",
                             "#FFDFA2",
                             "#FFA93F",
                             "#D5610D"))+
  theme(plot.margin=unit(c(0.1, 0.5, 0.1, 0.5),
                         "cm"),
        legend.position = "bottom",
        legend.title = element_blank(),
        legend.key.size = unit(0.2, 'cm'),
        text = element_text(size=4))
```

@@

library(patchwork)
(plot1 + plot4)/(plot2 + plot5)/(plot3 + plot6)
```

@@

```{r figure-masking-coordinates, echo = FALSE, out.width=c("29%","37%"), out.height="20%",fig.cap="\\label{fig:Anonymizing}(Left) Masking coordinates. Spatial range. (Right) Coordinate displacement in meters (Valencia)",fig.show='hold',fig.align='center'}
knitr::include_graphics(c("EPB_files/points-moved-image.png","EPB_files/coordinates-valencia.png"))
```

>>>>

```{r load-packages, include=FALSE}
library(dplyr) # A Grammar of Data Manipulation
library(ggplot2) # Create Elegant Data Visualisations Using the Grammar of Graphics
library(glue) # Interpreted String Literals
library(gridExtra) # Miscellaneous Functions for "Grid" Graphics
library(idealista18) # Idealista 2018 Data Package
library(kableExtra) # Construct Complex Table with 'kable' and Pipe Syntax
library(patchwork) # The Composer of Plots
library(sf) # Simple Features for R
library(xtable) # Export Tables to LaTeX or HTML
```

@@

This micro-data set can be used to benchmark new methods in a reproducible fashion  [e.g., @rey2024using]. Applied and theoretical researchers on real estate mass appraisal and valuation methods might use this dataset to canonically compare the performance of their proposed comparable and hedonic models, among others. The data can also be used to study the segmentation of housing submarkets and related topics such as the impact of suburban areas on house prices. The listings have been enriched with official information from the Spanish cadastre along with other relevant geographical features, such as distance to urban points of interest. In any case, the data might be easily extended by spatially joining other datasets that contain information at administrative, census tract, or postal code levels.

@@

plot6 <- ggplot(data = Valencia_prop) +
  geom_sf(aes(fill = Quantile),
          color = NA,
          size=.2) +
    geom_sf(data = Valencia_Polygons,
          fill = NA) +
  labs(caption = "Valencia districts: listings/total dwellings") +
  ylim(39.405,39.52) +
  theme_bw(base_size = 6) +
  scale_fill_manual(values=c("#FFFEDE",
                             "#FFDFA2",
                             "#FFA93F",
                             "#D5610D"))+
  theme(plot.margin=unit(c(0.1, 0.5, 0.1, 0.5),
                         "cm"),
        legend.position = "bottom",
        legend.title = element_blank(),
        legend.key.size = unit(0.2, 'cm'),
        text = element_text(size=4))

fig_01 <- ((plot1 + plot4)/(plot2 + plot5)/(plot3 + plot6))

ggsave(fig_01,
       filename = "main_EPB_figures/fig-01.jpeg",
       height = 6.5,
       units = "in")
```

@@

fig_01
```

@@

```{r figure-masking-coordinates, echo = FALSE, out.width=c("29%","37%"), out.height="20%",fig.cap="\\label{fig:Anonymizing}(Left) Masking coordinates. Spatial range. (Right) Coordinate displacement in meters (Valencia)",fig.show='hold',fig.align='center'}
knitr::include_graphics(c("main_EPB_figures/points-moved-image.jpeg","main_EPB_figures/coordinates-valencia.jpeg"))
```

### 2024-03-12 EPB/main_EPB.tex
Prepared files for final submission to production with EPB

This micro-data set can be used to benchmark new methods in a
reproducible fashion \citep[e.g.,][]{rey2023using}. Applied and
theoretical researchers on real estate mass appraisal and valuation
methods might use this dataset to canonically compare the performance of
their proposed comparable and hedonic models, among others. The data can
also be used to study the segmentation of housing submarkets and related
topics such as the impact of suburban areas on house prices. The
listings have been enriched with official information from the Spanish
cadastre along with other relevant geographical features, such as
distance to urban points of interest. In any case, the data might be
easily extended by spatially joining other datasets that contain
information at administrative, census tract, or postal code levels.

@@

{\centering \includegraphics[width=0.29\linewidth,height=0.2\textheight]{EPB_files/points-moved-image} \includegraphics[width=0.37\linewidth,height=0.2\textheight]{EPB_files/coordinates-valencia}

>>>>

This micro-data set can be used to benchmark new methods in a
reproducible fashion \citep[e.g.,][]{rey2024using}. Applied and
theoretical researchers on real estate mass appraisal and valuation
methods might use this dataset to canonically compare the performance of
their proposed comparable and hedonic models, among others. The data can
also be used to study the segmentation of housing submarkets and related
topics such as the impact of suburban areas on house prices. The
listings have been enriched with official information from the Spanish
cadastre along with other relevant geographical features, such as
distance to urban points of interest. In any case, the data might be
easily extended by spatially joining other datasets that contain
information at administrative, census tract, or postal code levels.

@@

{\centering \includegraphics[width=0.29\linewidth,height=0.2\textheight]{main_EPB_figures/points-moved-image} \includegraphics[width=0.37\linewidth,height=0.2\textheight]{main_EPB_figures/coordinates-valencia}
